О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
Fix the quantity of edges
A ref to the theorem about lattice

	The area of the triangle $M_1 M_3 M_4$ is rational because $|M_3 - M_4| \in \mathbb{Z}$.
	Thus, the set $M$ is of characteristic 1,
	and there is a Cartesian coordinate system such that $M_1=(-1/2,0)$, $M_2=(1/2,0)$, $M_3=(0, a/2)$.
	(TODO: ref?)
	It is clear that $a\neq 0$.
	We set $b = |M_1 - M_3|$ and $O=(0,0)$.
	Applying the Pythagorean theorem to triangle $OM_1M_3$, we obtain the following Diophantine equation:
	\begin{equation}
		\frac{1}{4} + \frac{a^2}{4} = b^2
		,
	\end{equation}
	or, which is the same,
	\begin{equation}
		1 + a^2 = (2b)^2
		,
	\end{equation}
	that has no integral solutions.
	This contradiction concludes the proof.
\end{proof}

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $m$
	not more than $1+\frac{m^2 - m}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-2)$-dimensional simplex.

>>>>

	The area of the triangle $M_1 M_3 M_4$ is rational because $|M_3 - M_4| \in \mathbb{Z}$.
	Thus, the set $M$ is of characteristic 1,
	and there is a Cartesian coordinate system such that $M_1=(-1/2,0)$, $M_2=(1/2,0)$, $M_3=(0, a/2)$
	(see~\cite[Theorem 4]{our-vmmsh-2018}).
	It is clear that $a\neq 0$.
	We set $b = |M_1 - M_3|$ and $O=(0,0)$.
	Applying the Pythagorean theorem to triangle $OM_1M_3$, we obtain the following Diophantine equation:
	\begin{equation}
		\frac{1}{4} + \frac{a^2}{4} = b^2
		,
	\end{equation}
	or, which is the same,
	\begin{equation}
		1 + a^2 = (2b)^2
		,
	\end{equation}
	that has no integral solutions.
	This contradiction concludes the proof.
\end{proof}

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $M$
	not more than $1+\frac{(m-1)^2 - (m-1)}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-2)$-dimensional simplex.
